Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/paper.tex
small change

Note that the absence, in our model, of measurement noise over $Y$, is not restrictive, so long $F$ has full-rank (or over $Img(F)$, the subspace spanned by the columns of $F$). In fact, adding $M$ as measurement noise on $Y$, we have $$Y=(XE+N)F+M$$ On $Img(F)$,
rewriting $M = MF^{-1}F$, we have
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$

@@

% I find a bit surprising to mention cauaslity literare in ML at the end. I would have expected this in the introduction to convince reviewer that know your stuff.
CONCLUSION SENTENCE

>>>>

Note that the absence, in our model, of measurement noise over $Y$, is not restrictive. Starting from a model with measurement noise $M$, $$Y=(XE+N)F+M$$ On $Img(F)$,
we can rewrite $M = MF^{-1}F$, and we have
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$
If $F$ has full rank, the

@@

% I find a bit surprising to mention cauaslity literare in ML at the end. I would have expected this in the introduction to convince reviewer that know your stuff.
